\documentclass[envcountsame,envcountchap]{ALMmono}

\usepackage{bm}
\usepackage{wrapfig}                  % 图文混排
\usepackage{picins}                   % 图文混排
\usepackage{sidecap}                  % 图注在单侧的宏包
\usepackage{picinpar}                 % 图文混排
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool

\usepackage{curves}
\usepackage{epic,eepic}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{epsfig}

\usepackage{amsbsy,amsmath}
\usepackage{rotating}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{amscd}
\usepackage{clrscode}

%\usepackage{algorithm2e}
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{mathptmx}
\usepackage{amscd}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{diagrams}
\usepackage{picinpar}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage[all]{xy}

\usepackage{CJK}
%\usepackage{titlesec}
%\usepackage{CJKpunct}
%\usepackage{CJKnumb}

\usepackage{listings}
%\usepackage{color}

\paperwidth 170truemm
\paperheight 228truemm
\textwidth 148truemm
\textheight 195truemm
%\headheight=1.5\ccht
\headsep=6truemm
\footskip=20pt
\topmargin=0pt
\oddsidemargin=0pt
\evensidemargin=0pt
\linespread{1.25}


\begin{CJK*}{GBK}{song}

% etc.
% see the list of further useful packages
% in the Reference Guide, Sects. 2.3, 3.1-3.3

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program


\makeatletter
\renewenvironment{thebibliography}[1]
%org     {\chapter*{\bibname
%org    \@mkboth{\MakeUppercase\bibname}{\MakeUppercase\bibname}}%
     {\chapter*{\bibname}%                            !!!
      \@mkboth{\bibname}{\MakeUppercase\bibname}
      \list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \small%                                               !!!
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{rem}[thm]{Remark}
\newtheorem{coro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{de}[thm]{Definition}
\newtheorem{hyp}[thm]{Hypothesis}

\newtheorem{nota}[thm]{Notation}
\newtheorem{ex}[thm]{Example}
%\newtheorem{proc}[thm]{Procedure}

\newtheorem{exer}[thm]{Exercise}

\newtheorem{prob}[thm]{Problem}

\def\refpp#1{(\ref{#1})}
%
%\def\refpp#1{(\ref{#1}){\tt{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%\titleformat{\part}{\centering\Huge\bfseries}{第\,\thepart \,卷}{1em}{}

\lstset{breaklines=true,numbers=left,numberstyle=\small,basicstyle=\footnotesize\ttfamily,frame=single,escapeinside=``,xleftmargin=2em,xrightmargin=2em, aboveskip=1em}

%keywordstyle=\color{blue!70},commentstyle=\color{red!50!green!50!blue!50},rulesepcolor=\color{red!20!green!20!blue!20}

\author{刘鹏}
\title{广告的秘密}
\subtitle{互联网计算广告技术}
\maketitle

\frontmatter%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{4cm}
\centerline{\Large \bf Dedicated to *****}
\thispagestyle{empty}
\newpage
\thispagestyle{empty}

\include{preface}
\setcounter{tocdepth}{4}
\tableofcontents%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 生成目录

\mainmatter%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 正文
\part{写给想从事互联网广告的朋友们}

\include{ch1}
\include{ch2}
\include{ch3}

\part{计算广告的今生前世}
\include{ch4}
\include{ch5}
\include{ch6}

\part{计算广告核心技术详解}
\include{ch7}
\include{ch8}
\include{ch9}
\include{ch10}
\include{ch11}
\include{ch12}

%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{GRC99}

\bibitem{Arens}
William F. Arens, \emph{Contemporary Advertising}, The McGraw-Hill, 2002

\bibitem{Audibert}
Jean Yves Audibert, Remi Munos, and Csaba Szepesvari, Use of variance estimation in the multi-armed bandit problem, \emph{NIPS'06}, Dec 2006

\bibitem{Bennet}
J. Bennet and S. Lanning, The Netflix Prize, \emph{KDD Cup and Workshop}, www.netflixprize.com, 2007.

\bibitem{Berger}
Adam Berger, Stephen A. Della Pietra, and Vincent J. Della Pietra, A Maximum Entropy Approach to Natural Language Processing, \emph{Computational Linguistics}, 22(1): 39-71, 1996

\bibitem{Bishop}
Christopher M. Bishop, \emph{Pattern Recognition and Machine Learning}, Springer, 2006

\bibitem{Blei}
David M. Blei, Andrew Y. Ng, and Micheal I. Jordan. Latent Dirichlet allocation. \emph{Journal of Machine Learning Research}, 3:993C1022, Jan. 2003

\bibitem{Boyd1}
Stephen Boyd, Lieven Vandenberghe, \emph{Convex Optimization}, Cambridge University Press, 2004

\bibitem{Boyd2}
Stephen Boyd, Neal Parikh, Eric Chu, Borja Peleato, and Jonathan Eckstein, \emph{Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers, Foundations and Trends in Machine Learning}, 3(1):  1C122, 2010

\bibitem{Broder}
Andrei Z. Broder, David Carmel, Michael Herscovici, Aya Soffer, and Jason Zien, Efficient query evaluation using a two-level retrieval process, \emph{CIKM'03} : 426C434, Nov. 2003

\bibitem{Canny}
John Canny, GaP: A factor model for discrete data, \emph{SIGIR'04}, July 2004

\bibitem{Chakraborty}
Tanmoy Chakraborty, Eyal Even-Dar, Sudipto Guha, Yishay Mansour, and S. Muthukrishnan, Selective call out and Real-time Bidding, \emph{WINE'10}: 145C157, Dec, 2010

\bibitem{Chen}
Ye Chen, Dmitry Pavlov, and John F. Canny, Large-scale behavioral targeting, \emph{KDD'09}: 426―434, June, 2009

\bibitem{Chen2}
Peiji Chen, etc., Ad Serving Using a Compact Allocation Plan, \emph{*}, 2012.

\bibitem{Cui}
Ying Cui, Ruofei Zhang, Wei Li, and Jianchang Mao, Bid landscape forecasting in online ad exchange marketplace, \emph{KDD'11}, Aug, 2011

\bibitem{Dean}
Jeffrey Dean and Sanjay Ghemawat, MapReduce: Simplied Data Processing on Large Clusters, \emph{OSDI'04}, Dec, 2004

\bibitem{Dempster}
A. P. Dempster, N. M. Laird and D. B. Rubin, ``Maximum likelihood from incomplete data via the EM algorithm," \emph{J. Royal Statist. Society (B)}, 39, pp. 1-38, 1977.

\bibitem{Edelman}
Benjamin Edelman, Michael Ostrovsky, and Michael Schwarz, Internet advertising and the generalized second-price auction: selling billions of dollars worth of keywords, \emph{American Economic Review}, 97:242-259, 2005

\bibitem{Feldman}
Jon Feldman, Nitish Korula, Vahab Mirrokni, S. Muthukrishnan, and Martin Pal, Online ad assignment with free disposal, \emph{WINE'09}: 374C385, Dec, 2009

\bibitem{Gates}
Alan F. Gates, etc., Pig: A Structured, High-Level Dataflow System for Hadoop,  …

\bibitem{Ghemawat}
Sanjay Ghemawat, Howard Gobioff, and Shun-Tak Leung, The Google File System, \emph{SOSP'03}, Oct, 2003

\bibitem{Ghosh}
Arpita Ghosh, Preston McAfee, Kishore Papineni, and Sergei Vassilvitskii. Representative allocations for guaranteed display advertising. \emph{Manuscript}, 2009.

\bibitem{Gill}
Jeff Gill, \emph{Generalized Linear Model: A Unified Approach}, SAGE publications, 2000

\bibitem{Gittins}
J. Gittins. Bandit processes and dynamic allocation indices, J. of the Royal Stat. \emph{Society}, B(41), 1979

\bibitem{Hofmann}
Thomas Hofmann, Probabilistic latent semantic indexing, \emph{SIGIR'09}: 50-57, 1999

\bibitem{Jansen}
Bernard J. Jansen and Tracy Mullen, Sponsored search: an overview of the concept, history, and technology, \emph{Int. J. Electronic Business}, 6(2): 114-131, 2008

\bibitem{Jordan}
Michael I. Jordan, Zoubin Ghahramani, Tommi S. Jaakkola, and Lawrence K. Saul, An introduction to variational methods for graphical models, \emph{Machine Learning}, 37: 183C233, 1999

\bibitem{Koren}
Yehuda Koren, Factorization meets the neighborhood: a multifaceted collaborative filtering model, \emph{KDD'08}: 426C434, Aug. 2008

\bibitem{King}
Gary King, Lanche Zeng, Logistic regression in rare events data, \emph{Political Analysis}, 39(2):137-163, 2001

\bibitem{Lamport}
Leslie Lamport, Paxos made simple. \emph{SIGACT News}, 32(4):51C58, Dec. 2001

\bibitem{Li}
Lihong Li, Wei Chu, John Langford, and Robert E. Schapire, A contextual-bandit approach to personalized news article recommendation, \emph{WWW'10}: 661-670, Apr. 2010

\bibitem{Lin}
Chih-Jen Lin, Ruby C.Weng, and S. Sathiya Keerthi, Trust Region Newton Method for Large-Scale Logistic Regression, \emph{Journal of Machine Learning Research}, 9:627C650, 2008

\bibitem{MacKay}
David J.C. MacKay, \emph{Information Theory, Inference, and Learning Algorithms}, Cambridge University Press, 2003

\bibitem{Malouf}
Robert Malouf, A comparison of algorithms for maximum entropy parameter estimation, \emph{Proc. 6th Conference on Natural Language Learning} : 1C7, 2002

\bibitem{Markowitz}
Harry M. Markowitz, \emph{Portfolio Selection Efficient Diversification of Investments}, John Wiley \& Sons, Inc., New York Chapman \& Halll, Limited, London, 1959

\bibitem{Abhilasha_Mehta}
Abhilasha Mehta and Scott C. Purvis, Evaluating Advertising Effectiveness Through Advertising Response Modeling (ARM), \emph{1994 Advertising and Consumer Psychology Conference}, May, 1994

\bibitem{Aranyak_Mehta}
Aranyak Mehta, Amin Saberi, Umesh Vazirani, and Vijay Vazirani. Adwords and generalized online matching. \emph{J. ACM}, 54(5):22, 2007.

\bibitem{Narayanan}
Arvind Narayanan, Vitaly Shmatikov, Robust De-anonymization of Large Sparse Datasets, \emph{Proc. 2008 IEEE Symposium on Security and Privacy}, 111C-125, 2008.

\bibitem{Nocedal}
Jorge Nocedal, Stephen J. Wright, \emph{Numerical Optimization}, Springer, 1999

\bibitem{Olston}
Christopher Olston, Benjamin Reed, Utkarsh Srivastava, Ravi Kumar, and Andrew Tomkins, Pig Latin: A Not-So-Foreign Language for Data Processing, \emph{SIGMOD'08}: 1099-1110, June, 2008

\bibitem{Perotte}
Adler Perotte, Nicholas Bartlett, Noemie Elhadad, and Frank Wood, Hierarchically Supervised Latent Dirichlet Allocation, \emph{NIPS'11}, December, 2011

\bibitem{Slee}
Mark Slee, Aditya Agarwal, and Marc Kwiatkowski, Thrift: Scalable Cross-Language Services Implementation, Facebook, Apr, 2007

\bibitem{Su}
Xiaoyuan Su and Taghi M. Khoshgoftaar, A Survey of Collaborative Filtering Techniques, \emph{Advances in Artificial Intelligence}, Hindawi Publishing, Aug, 2009

\bibitem{Varian}
Hal R. Varian, Position auctions. \emph{International Journal of Industrial Organization}, 25:1163C1178, 2007

\bibitem{Vee}
Erik Vee, Sergei Vassilvitskii, and Jayavel Shanmugasundarum, Optimal online assignment with forecasts. \emph{Proc. of the ACM Conf. on
Electronic Commerce}, 2010

\bibitem{Wang}
Xuerui Wang, Andrei Broder, Marcus Fontoura, and Vanja Josifovski, A search-based method for forecasting ad impression in contextual advertising, \emph{WWW'09}: 491-500, Apr. 2009

\bibitem{Whang}
Steven Euijong Whang and Hector Garcia-Molina, Indexing Boolean Expressions, \emph{VLDB'09}, Aug, 2009

\bibitem{Zaharia}
Matei Zaharia, Mosharaf Chowdhury, Justin Ma, Michael J. Franklin, Scott Shenker, and Ion Stoica, Spark: Cluster Computing with Working Sets.

%\bibitem{alperin1}Alperin, J. L.; Bell, Rowen B.,ll Groups and representations. Graduate Texts in Mathematics, 162. Springer-Verlag, New York, 1995.

\end{thebibliography}

\end{CJK*}

\end{document}

%%%%%%%
\ddot{}
